environmenal/exploratory analysis

### 2023-05-11 03_exploratory.Rmd
added functions
bathymetry slope and depth extraction from TIF

---
title: "exploratory analysis"
output: html_document
date: "2022-11-06"
---

Required Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(sf)
library(rerddap)
library(terra)
library(marmap)
library(rnaturalearth)
library(mapproj)
library(raster)
#library("rerddapXtracto")
library(PAMpal)
library(PAMmisc)
library(maptiles)
library(tmap)
library(spData)
library(tmaptools)
library(grid)
library(ggspatial)
```

Create sf objects and basemaps for maps
```{r}
whales_8_10sf <- BWsf %>%                            
dplyr::filter(station == "8" | station == "10")

trackssf <- st_as_sf(tracks, coords = c("Longitude", "Latitude"), crs=4326)
trk_TOL_08 <- st_as_sf(tracks_SS_08, coords = c("Longitude", "Latitude"), crs=4326)
trk_TOL_10 <- st_as_sf(tracks_SS_10, coords = c("Longitude", "Latitude"), crs=4326)
trackBase <- get_tiles(whales_8_10sf, provider = "Esri.WorldShadedRelief")
allTrackbase <- get_tiles(trackssf, provider = "Stamen.TonerLite", zoom = 5)
```
### Exploratory analysis

SST from PAMPal
```{r}
# Downloads data from servers, uncomment and only run once
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'jplMURSST41', fileName = "analysedSST")

# from file 
tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'data/analysedSST.nc') %>%
  rename(., sst_mean = analysed_sst_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)   # rename new column to "sst_mean" and remove unnecessary columns
```

Distance to continental slope
```{r}
# Increase cell size by 30x to be visible
bathy <- rast("data/gebco_bathy.tif")
agg <- terra::aggregate(bathy, 5)
plot(agg)

# Rasterize track with agg as the template

#TOL_rast <- rasterize(trk_TOL_08, agg, field = "TOL_125")
sf08 <- st_as_sf(tracks_SS_08, coords = c("Longitude", "Latitude"), crs=4326, remove=F)
sf10 <- st_as_sf(tracks_SS_10, coords = c("Longitude", "Latitude"), crs=4326, remove=F)
trkraster08 <- rasterize(vect(sf08), agg)
trkraster10 <- rasterize(vect(sf10), agg)

# Map the coastline and cont. slope
cont <- st_as_sf(as.contour(bathy))
coast <- cont %>% filter(level == 0)
cont_slope <- cont %>% filter(level == -2000)
cont_slope_rast <- rasterize(cont_slope, agg, field = "level")
plot(cont_slope_rast, col = "red")
cont_slope_rast <- rasterize(cont_slope, agg)
plot(cont_slope_rast, col = "red")

#ggplot() + 
#  geom_raster(data = bathy_df, 
#              mapping = aes(x=x, y=y, 
#                            alpha = 0.8,
#                            fill = `gebco_bathy`))+
#  geom_sf(data = cont, col="black") + 
#  geom_sf(data = coast, col = "red") +
#  geom_sf(data = cont_slope, col = "purple") +
#  geom_sf(data = whales_8_10sf, mapping = aes()) +
#  scale_color_gradient(low="green", high="red") 
```

### Extract slope_dist and bind to drift tracks
```{r}
# Drift 8
slopedist <- terra::distance(trkraster08, vect(cont_slope))     # measure distance from track to slope
extdist <- terra::extract(slopedist, vect(sf08))       # extract this distance into a df
tracks_SS_08 <- cbind(sf08,extdist) %>%                     # bind to main df
  dplyr::select(-ID) %>%
  rename("dist2slope" = gebco_bathy) %>%
  st_set_geometry(NULL)                         # Drop geometry to make df for future cbinds

#Drift 10
slopedist <- terra::distance(trkraster10, vect(cont_slope))     # measure distance from track to slope
extdist <- terra::extract(slopedist, vect(sf10))       # extract this distance into a df
tracks_SS_10 <- cbind(sf10,extdist) %>%                     # bind to main df
  dplyr::select(-ID) %>%
  #rename("dist2slope" = gebco_bathy) %>%
  st_set_geometry(NULL)                        # Drop geometry to make df for future cbinds
```

#### Bathymetry - PAMpal
```{r}
# Downloads from server
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'srtm15plus', fileName='depth.nc')

# Pulls from downloaded file
tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'data/depth.nc') %>%
  rename(., depth = z_mean) %>%        # rename new column to "depth"
  mutate(depth = depth*-1) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)
```

#### Bathymetric slope

```{r}
# Slope (Hard-coded - can fix this)
bgo <- getNOAA.bathy(lon1 = -121, lon2 = -131,
                     lat1 = 34, lat2= 40, resolution = 1)  # plot bounding box around drift 8 and 10
# As raster
bgo_rast <- marmap::as.raster(bgo)
bgo_slope <- terrain(bgo_rast, v = "slope")

# Extract slope values at points along drift 8
slope <- raster::extract(bgo_slope, tracks_SS_08[,4:3])
tracks_SS_08 <- cbind(tracks_SS_08, slope)
```

#### Distance from coast - PAMPal
Need to have variable choose itself!! Also, how do I get it to not download each time?
```{r}
#dist2shore <- erddapToEdinfo(dataset='dist2coast_1deg',
#                             baseurl='https://pae-paha.pacioos.hawaii.edu/erddap/',
#                             chooseVars = FALSE)

tracks_SS_08 <- matchEnvData(tracks_SS_08, nc='data/Dist2Shore.nc') %>%
  rename(., dist2shore = dist_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

#May not need this part
# Downloads from server
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'dist2coast_1deg', fileName='dist2coast.nc', var = 'dist')

# Pulls from downloaded file
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'data/dist2coast.nc')

# Downloads nc file
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc=dist2shore, fileName='Dist2Shore.nc')  
```

### Chlorophyll from PAMPal
```{r}
# Downloads from server
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdMH1chlamday', fileName='chlorophyll.nc')

# Pulls from downloaded file
tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'data/chlorophyll.nc')
```

#### Sea Surface Height Anomalies from PAMPal
```{r}
# Downloaded from server
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'nesdisSSH1day', fileName='sshanomalies.nc')

# Pulled from downloaded nc file
tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'data/sshanomalies.nc') %>%
  rename(., ssh_mean = sla_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)
```

### Wind Stress Curl from PAMPal *** NEEDS FIXING ****
```{r}
# Downloads from server
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdQMstress1day_LonPM180', fileName='erdQMstress1day_LonPM180.nc', var = 'curl')

# Pulls from downloaded file
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdQMstress1day_LonPM180.nc')
#tracks_SS_08

@@

#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc=windcurl, fileName='windcurl.nc')  
```

#### HyCOM Data - MLDepth, MLTemp, TTemp, TDepth, Salinity
Doesn't bin itself into separate dataframe based on size!
```{r}
# These refer to nc files that have already been downloaded from the server.
# Uncomment and only run once! Rows are hard-coded.

#hycomData0 <- matchEnvData(as.data.frame(tracks_SS_08[1:250,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm0.nc")

#hycomData1 <- matchEnvData(as.data.frame(tracks_SS_08[251:500,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm1.nc")

#hycomData2 <- matchEnvData(as.data.frame(tracks_SS_08[501:750,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm2.nc")

#hycomData3 <- matchEnvData(as.data.frame(tracks_SS_08[751:1200,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm3.nc")

#hycomData4 <- matchEnvData(as.data.frame(tracks_SS_08[1201:1500,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm4.nc")

#hycomData5 <- matchEnvData(as.data.frame(tracks_SS_08[1501:1800,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm5.nc")

#hycomData6 <- matchEnvData(as.data.frame(tracks_SS_08[1801:2145,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm6.nc")

#hycomData7 <- matchEnvData(as.data.frame(tracks_SS_08[2146:2469,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm7.nc")

#hycomData8 <- matchEnvData(as.data.frame(tracks_SS_08[2470:2769,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "hycomm8.nc")

# Run the 9 nc lists that make up tracks_SS_08
hycomData0 <- matchEnvData(as.data.frame(tracks_SS_08[1:250,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm0.nc")
hycomData1 <- matchEnvData(as.data.frame(tracks_SS_08[251:500,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm1.nc")
hycomData2 <- matchEnvData(as.data.frame(tracks_SS_08[501:750,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm2.nc")
hycomData3 <- matchEnvData(as.data.frame(tracks_SS_08[751:1200,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm3.nc")
hycomData4 <- matchEnvData(as.data.frame(tracks_SS_08[1201:1500,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm4.nc")
hycomData5 <- matchEnvData(as.data.frame(tracks_SS_08[1501:1800,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm5.nc")
hycomData6 <- matchEnvData(as.data.frame(tracks_SS_08[1801:2145,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm6.nc")
hycomData7 <- matchEnvData(as.data.frame(tracks_SS_08[2146:2469,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm7.nc")
hycomData8 <- matchEnvData(as.data.frame(tracks_SS_08[2470:2769,]), var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, nc = "hycomm8.nc")
```

@@

Use above function on the smaller hycom datasets (0-6)
```{r}
#calcThermoVars(hycomData[[1]]$matchDepth, hycomData[[1]]$water_temp, plot=TRUE)

>>>>

---
title: "environmenal/exploratory analysis"
output: html_document
date: "2022-11-06"
---

Required Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sf)
#library(raster)
library(terra)
library(PAMpal)
library(PAMmisc)
#library(marmap)
library(rerddap)
```

### Get Environmental Variables

For each buoy, the value of each environmental variable will be added to each track point based on Lat, Long, and UTC.
Data only need to be downloaded once. After that, can refer to the file in the external hard drive ("D:").

Environmental variables: Sea surface temp, Wind stress curl, Distance to continental slope, Depth, bathymetric slope,
distance to shore, chlorophyll, sea surface height anomalies, + Hycom variables.

Sea Surface Temperature from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST07", var = c('analysed_sst'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST08", var = c('analysed_sst'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST10", var = c('analysed_sst'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST12", var = c('analysed_sst'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST13", var = c('analysed_sst'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST14", var = c('analysed_sst'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST16", var = c('analysed_sst'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST18", var = c('analysed_sst'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST19", var = c('analysed_sst'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST20", var = c('analysed_sst'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST21", var = c('analysed_sst'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST22", var = c('analysed_sst'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'jplMURSST41', fileName = "D:/Environ_variables/analysedSST23", var = c('analysed_sst'))
```

Once downloaded, matches SST from file
```{r}
SSTlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="analysedSST")

for (ss in SSTlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(ss, 33, 34))), nc = ss) %>%
  rename(., sst_mean = analysed_sst_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)   # rename new column to "sst_mean" and remove unnecessary columns

  assign(paste0("tracks_SS_", substr(ss, 33, 34)), data)
}
```
### Wind Stress Curl from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress07.nc", var = c('curl'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress08.nc", var = c('curl'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress10.nc", var = c('curl'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress12.nc", var = c('curl'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress13.nc", var = c('curl'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress14.nc", var = c('curl'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress16.nc", var = c('curl'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress18.nc", var = c('curl'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress19.nc", var = c('curl'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress20.nc", var = c('curl'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress21.nc", var = c('curl'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress22.nc", var = c('curl'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'erdQAstress1day', fileName = "D:/Environ_variables/windstress23.nc", var = c('curl'))

# Pulls from downloaded file
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'data-raw/erdQMstress1day_LonPM180.nc')
#tracks_SS_08

@@

#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc=windcurl, fileName='windcurl.nc')

```
Once downloaded, matches wind stress curl from file
```{r}
windlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="windstress")

for (w in windlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(w, 32, 33))), nc = w) %>%
     dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean, -matchDepth_mean)   # remove unnecessary columns

  assign(paste0("tracks_SS_", substr(w, 32, 33)), data)
}
```

### Distance to continental slope (uses terra package)
```{r}
bathy <- rast("D:/CCES_gebco_bathy.tif") # Bathymetry for all of CCE from https://download.gebco.net/
agg <- terra::aggregate(bathy, 5)  # Increase cell size by factor of 5 to be visible

cont <- st_as_sf(as.contour(bathy, )) # Create contour lines from bathymetry 
cont_slope <- cont %>% filter(level == -2000) # Establish continental shelf. Is 2000m the correct depth for continental shelf?

tracklist <- grep(pattern = "tracks_SS_", names(.GlobalEnv), value = T)

for (t in tracklist) {
  sf <- st_as_sf(get(t), coords = c("Longitude", "Latitude"), crs=4326, remove=F)
  trk <- terra::rasterize(vect(sf), agg)
  slop <- terra::distance(trk, vect(cont_slope))
  ext <- terra::extract(slop, vect(sf))

  dbind <- cbind(sf, ext) %>%
  dplyr::select(-ID) %>%
  rename("dist2slope" = last) %>%
  st_set_geometry(NULL) # remove geometry to prevent buoy dataframe from becoming sf object for future

  assign(paste0("tracks_SS_", substr(t, 11, 12)), dbind)
}
```

Depth from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth07.nc", var = c('z'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth08.nc", var = c('z'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth10.nc", var = c('z'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth12.nc", var = c('z'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth13.nc", var = c('z'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth14.nc", var = c('z'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth16.nc", var = c('z'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth18.nc", var = c('z'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth19.nc", var = c('z'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth20.nc", var = c('z'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth21.nc", var = c('z'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth22.nc", var = c('z'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'srtm15plus', fileName = "D:/Environ_variables/depth23.nc", var = c('z'))
```

Once downloaded, matches depth from file
```{r}
depthlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="depth")

for (dd in depthlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(dd, 27, 28))), nc = dd) %>%
  rename(., depth = z_mean) %>%        # rename new column to "depth"
  mutate(depth = depth*-1) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(dd, 27, 28)), data)
}
```

#### Bathymetric slope (skipping loop for now)
```{r}
bathy_slope <- terra::terrain(bathy, v = "slope")

for (t in tracklist) {
  slope <- terra::extract(bathy_slope, get(t)[,4:3]) %>%  # Reads latitude and longitude of buoy dataframe
  dplyr::select(-ID) %>%
  rename("bathy_slope" = slope)

  sbind <- cbind(get(t), slope)

  assign(paste0("tracks_SS_", substr(t, 11, 12)), sbind)
}
```

Distance to Shore from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore07.nc", var = c('dist'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore08.nc", var = c('dist'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore10.nc", var = c('dist'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore12.nc", var = c('dist'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore13.nc", var = c('dist'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore14.nc", var = c('dist'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore16.nc", var = c('dist'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore18.nc", var = c('dist'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore19.nc", var = c('dist'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore20.nc", var = c('dist'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore21.nc", var = c('dist'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore22.nc", var = c('dist'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'dist2coast_1deg', fileName = "D:/Environ_variables/dist2shore23.nc", var = c('dist'))
```

Once downloaded, matches Distance to Shore from file
```{r}
distlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="dist2shore")

for (d2 in distlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(d2, 32, 33))), nc = d2) %>%
  rename(., dist2shore = dist_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(d2, 32, 33)), data)
}
```

### Chlorophyll from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll07.nc", var = c('chlorophyll'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll08.nc", var = c('chlorophyll'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll10.nc", var = c('chlorophyll'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll12.nc", var = c('chlorophyll'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll13.nc", var = c('chlorophyll'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll14.nc", var = c('chlorophyll'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll16.nc", var = c('chlorophyll'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll18.nc", var = c('chlorophyll'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll19.nc", var = c('chlorophyll'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll20.nc", var = c('chlorophyll'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll21.nc", var = c('chlorophyll'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll22.nc", var = c('chlorophyll'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'erdMH1chlamday', fileName = "D:/Environ_variables/chlorophyll23.nc", var = c('chlorophyll'))
```

Once downloaded, matches chlorophyll from file
```{r}
chlalist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="chlorophyll")

for (ch in chlalist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(ch, 33, 34))), nc = ch) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(ch, 33, 34)), data)
}
```

Sea Surface Height Anomalies from ERDDAP using PAMPal function
```{r}
# Downloads data from servers onto external hard drive. Uncomment and only run once.
#tracks_SS_07 <- matchEnvData(tracks_SS_07, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh07.nc", var = c('sla'))
#tracks_SS_08 <- matchEnvData(tracks_SS_08, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh08.nc", var = c('sla'))
#tracks_SS_10 <- matchEnvData(tracks_SS_10, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh10.nc", var = c('sla'))
#tracks_SS_12 <- matchEnvData(tracks_SS_12, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh12.nc", var = c('sla'))
#tracks_SS_13 <- matchEnvData(tracks_SS_13, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh13.nc", var = c('sla'))
#tracks_SS_14 <- matchEnvData(tracks_SS_14, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh14.nc", var = c('sla'))
#tracks_SS_16 <- matchEnvData(tracks_SS_16, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh16.nc", var = c('sla'))
#tracks_SS_18 <- matchEnvData(tracks_SS_18, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh18.nc", var = c('sla'))
#tracks_SS_19 <- matchEnvData(tracks_SS_19, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh19.nc", var = c('sla'))
#tracks_SS_20 <- matchEnvData(tracks_SS_20, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh20.nc", var = c('sla'))
#tracks_SS_21 <- matchEnvData(tracks_SS_21, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh21.nc", var = c('sla'))
#tracks_SS_22 <- matchEnvData(tracks_SS_22, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh22.nc", var = c('sla'))
#tracks_SS_23 <- matchEnvData(tracks_SS_23, nc = 'nesdisSSH1day', fileName = "D:/Environ_variables/ssh23.nc", var = c('sla'))
```

Once downloaded, matches sea surface height anomalies from file
```{r}
sshlist <- dir("D:/Environ_variables", recursive=TRUE, full.names=TRUE, pattern="ssh")

for (sh in sshlist) {
  data <- matchEnvData(get(paste0("tracks_SS_", substr(sh, 25, 26))), nc = sh) %>%
  rename(., ssh_mean = sla_mean) %>%
  dplyr::select(-matchLong_mean, -matchLat_mean, -matchTime_mean)

  assign(paste0("tracks_SS_", substr(sh, 25, 26)), data)
}
```

#### HyCOM Data - MLDepth, MLTemp, TTemp, TDepth, Salinity

@@

```{r}
# Create loop for each buoy to download HYCOM data

##FIX THIS - try testing on ONE buoy
for (t in tracklist) {
  Hdata <- matchEnvData(as.data.frame(get(paste0("tracks_SS_", substr(t, 11, 12)))), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)

  thermData <- bind_rows(lapply(Hdata, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))
  bindr <- cbind(get(paste0("tracks_SS_", substr(t, 11, 12))), thermData)
  assign(paste0("tracks_SS_", substr(t, 11, 12)), bindr) #fix this part?
}
```

```{r}
test08 <- matchEnvData(as.data.frame(tracks_SS_08), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)

thermData08 <- bind_rows(lapply(test08, function(x) {
    # do thermo calcs
    result <- calcThermoVars(x$matchDepth, x$water_temp)
    # get specific values
    result$temp400 <- x$water_temp[x$matchDepth == 400]
    result$sal400 <- x$salinity[x$matchDepth == 400]
    result
}))

tracks_SS_08 <- cbind(tracks_SS_08, thermData08)
```

```{r}
#hycomData0 <- matchEnvData(as.data.frame(tracks_SS_08[1:250,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm0.nc")

#test <- matchEnvData(as.data.frame(tracks_SS_07), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000)

#hycomData1 <- matchEnvData(as.data.frame(tracks_SS_08[251:500,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm1.nc")

#hycomData2 <- matchEnvData(as.data.frame(tracks_SS_08[501:750,]), nc=PAMmisc::hycomList, var=c('water_temp', 'salinity'), raw=TRUE, depth = 0:1000, fileName = "data-raw/hycomm2.nc")
